Bullet Groups as a test of $\Lambda$CDM

### 2014-02-27 paper/ms.tex
empezando a estructurar el texto

The analysis presented in this paper uses mainly the Bolshoi (250
Mpch$^{-1}$ simulation box, 1 kpch$^{-1}$ resolution) Database
simulation described in \citet{2011ApJ...740..102K}. The simulation
follows the evolution of 8.6 billion particle cosmological N-body
simulation from z=80 to z=0 in a comoving cube of $250$ Mpch$^{-1}$
on a side. The cosmology used  corresponds to  the spatially flat
concordance model with the following parameters:  the density
parameter for matter (dark matter$+$baryons) $\Omega_m=0.27$, the
density parameter for baryonic matter  $\Omega_b=0.0469$, the density
parameter for dark energy $\Omega_{\Lambda}=0.73$, the Hubble
parameter $h=0.7$, the 
normalization of the Power spectrum $n=0.95$ and the amplitude of mass
density fluctuation (at redshift z$=$0) $\sigma_8=0.82$.  The number
of particles used for each of the DM component was $2048^3$, resulting
in a mass resolution of $1.35 \times 10^8$ M$_{\odot}$h$^{-1}$.

>>>>

We use the Bolshoi Run, a cosmological DM only simulation over a cubic
volume of 250 comoving \hMpc on a side. The simulation uses the ART code to
follow the evolution of  a dark matter density field sampled with
$2024^3$ from $z=80$ to $z=0$ [...]. The cosmology used  corresponds to  the spatially flat
concordance model with the following parameters:  the density
parameter for matter (dark matter$+$baryons) $\Omega_m=0.27$, the
density parameter for baryonic matter  $\Omega_b=0.0469$, the density
parameter for dark energy $\Omega_{\Lambda}=0.73$, the Hubble
parameter $h=0.7$, the 
normalization of the Power spectrum $n=0.95$ and the amplitude of mass
density fluctuation (at redshift z$=$0) $\sigma_8=0.82$.  The number
of particles used for each of the DM component was $2048^3$, resulting
in a mass resolution of $1.35 \times 10^8$ M$_{\odot}$h$^{-1}$.

\citet{2011ApJ...740..102K}.
